Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \label{eqn:hv:type1:R_i'}
}
Computing the ``segment $h_\bot$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version, with $H$ and $R_i$ as the input). By symmetry, so is the computation of $h_\top, v_\vdash$, and $v_\dashv$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(kn \log n)$ total time.

@@

By statements (1) and (2) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, the above algorithm runs in $O(1 + |\J(R'_1, ..., R'_{k-2})| + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time, where the derivation used \eqref{eqn:hv:type1:J*} and Lemma~\ref{lmm:hv:type1:recur-output}.

>>>>

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \label{eqn:hv:type1:R_i'}
}
Computing the ``segment $h_\bot$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version, with $H$ and $R_i$ as the input). By symmetry, so is computing the $h_\top, v_\vdash$, and $v_\dashv$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(kn \log n)$ total time.

@@

By statements (1) and (2) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, the above algorithm runs in $O(1 + k \cdot |\J(R'_1, ..., R'_{k-2})| + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time, where the derivation used \eqref{eqn:hv:type1:J*} and Lemma~\ref{lmm:hv:type1:recur-output}.
